Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-09 papers/B1555_EdgeOn/B1555_letter.tex
Fixed small typos

1\documentclass[manuscript]{emulateapj}

@@

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The position of lens galaxy is at $(-0.1620, -0.2401)$. Model best-fit parameters are stated as following. 
SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degree$. 
Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degree, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.

>>>>

\documentclass[manuscript]{emulateapj}

@@

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The position of lens galaxy is at $(-0.1620, -0.2401)$. Model best-fit parameters are stated as following. 
SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degr$. 
Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degr, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.
